\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-03 paper/sp.tex
figures

We adopt 9~percent as the method's precision.
This estimate is conservative in that the 9-percent scatter includes contributions
from both our spectrophotometric model and from the \gaia\ measurements themselves.
However this estimate is not so conservative in that the test is performed with
\gaia's best stars, which are bright, nearby, in low extinction regions, and
(because of these things) near Solar metallicity.
There could in principle be additional bias or scatter for stars that are in dustier
regions or at lower metallicities.
\figurename~HOGG WHAT FIGURE shows that
there is no suggestion of any such trends when we color the residuals by metallicity
or $H-W_2$ color (which is a reddening proxy).

Another validation of the results can be obtained by looking at known
clusters or spatially compact objects in the data.
In HOGG WHAT FIGURE, we show the parallax distribution from \gaia\ and
the spectrophotometric-parallax distribution from this work for stars in
angular proximity to known stellar clusters and the Sagittarius dwarf
galaxy.
These clusters span some range in metallicity and age, and therefore test
the accuracy of the method for different kinds of populations.
They show that both \gaia\ and the spectrophotometric parallaxes appear to be unbiased
for these clusters and the range in abundances and ages they represent.
HOGG: DO WE NEED TO ADDRESS whether why not these clusters show 9-percent spreads?

@@

HOGG: Similarly, the spectral part of the model should also be
interpretable. HOGG SHOW FIGURE THAT DEMONSTRATES THIS, qualitatively.

@@

What is this useful for and how do you use them safely?
HOGG: Show a map of the kinematic rotation of the Galaxy as a function of
x and y, colored by metallicity.
We see the kinematic center of the Galaxy! We see the rotation curve.
We see the chemical gradients.

>>>>

We adopt 9~percent as the method's precision.
This estimate is conservative in that the 9-percent scatter includes contributions
from both our spectrophotometric model and from the \gaia\ measurements themselves.
However this estimate is not so conservative in that the test is performed with
\gaia's best stars, which are bright, nearby, in low extinction regions, and
(because of these things) near Solar metallicity.
There could in principle be additional bias or scatter for stars that are in dustier
regions or at lower metallicities.
\figurename~\ref{fig:residuals} shows that
there is no suggestion of any such trends when we color the residuals by metallicity
or $H-W_2$ color (which is a reddening proxy).
\begin{figure}
\caption{Prediction residuals colored by relevant features.
  Each panel shows the prediction residuals (\gaia\ astrometric parallax minus
  spectrophotometric parallax $\gparallax_n-\sparallax_n$) colored by a different
  data feature that might be relevant to the residual.\label{fig:residuals}}
\end{figure}

Another validation of the results can be obtained by looking at known
clusters or spatially compact objects in the data.
In \figurename~\ref{fig:clusters}, we show the parallax distribution from \gaia\ and
the spectrophotometric-parallax distribution from this work for stars in
angular proximity to known stellar clusters and the Sagittarius dwarf
galaxy.
These clusters span some range in metallicity and age, and therefore test
the accuracy of the method for different kinds of populations.
They show that both \gaia\ and the spectrophotometric parallaxes appear to be unbiased
for these clusters and the range in abundances and ages they represent.
HOGG: DO WE NEED TO ADDRESS whether why not these clusters show 9-percent spreads?
\begin{figure}
\caption{The histograms of \gaia\ astrometric parallaxes $\gparallax_n$
  and spectrophotometric parallaxes $\sparallax_n$ for stars in angular proximity
  to various stellar clusters in the \apogee\ observing footprint. In each panel,
  the expected parallax of the cluster is shown as a vertical line.\label{fig:clusters}}
\end{figure}

@@

HOGG: Similarly, the spectral part of the model should also be
interpretable. HOGG DESCRIBE \figurename~\ref{fig:spectral} THAT
DEMONSTRATES THIS, qualitatively.
\begin{figure}
\caption{The coefficients of the spectral part of the linear model.\label{fig:spectral}}
\end{figure}

@@

What is this useful for and how do you use them safely?
HOGG: Show a map of the kinematic rotation of the Galaxy as a function of
x and y, colored by metallicity in \figurename~\ref{fig:disk}.
We see the kinematic center of the Galaxy! We see the rotation curve.
We see the chemical gradients.
\begin{figure}
\caption{A map of the kinematics and element abundances in the Milky Way disk.
  This map shows HOGG SOMETHING.\label{fig:disk}}
\end{figure}
